FIXME

### 2013-09-20 writeups/proposal/proposal.tex
removed a few fixmes
Former-commit-id: 53bd91cd0417f301e2adc52aa359b82ae5b61af5 [formerly df127ee6acfa18f0e42b2a60b97489977f562984]
Former-commit-id: ecc91681c821569ec865b3689754fe4ca0616868

%\usepackage[compact]{titlesec}

\usepackage{tabu}
\usepackage{amssymb,amsmath}
\usepackage{setspace}

@@

% FIXME: Use better tweet figures
\begin{figure}[!htbp]
  \hfill
  \subfigure[]{\includegraphics[width=8cm]{twitterTweetExample1.pdf}}
  \hfill
  \subfigure[]{\includegraphics[width=8cm]{twitterTweetExample2.pdf}}
  \hfill
  \caption{Example tweets on Twitter.com}
  \label{figTweetExample}
\end{figure}

FIXME: Write summary paragraph for twitter tweets figures.

@@

\begin{figure}[!htbp]
  \scalebox{.4}{\resizebox{\linewidth}{!}{\includegraphics{google+HashtagExample.pdf}}}
  \caption{Example post on google+. The system recommended \emph{\#SFGiants} and \emph{\#BusterPosey} as hashtags for the user-generated post}
  \label{figGoogle+Hashtags}
\end{figure}

>>>>

%\usepackage[compact]{titlesec}
\usepackage{tabu}
\usepackage{amssymb,amsmath}
\usepackage{setspace}

@@

\begin{figure}[!htbp]
  {%
    \setlength{\fboxsep}{0pt}%
    \setlength{\fboxrule}{1pt}%
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample1-crop.pdf}}}
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample3-crop.pdf}}}
    \hfill
    \vfill
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample4-crop.pdf}}}
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample5-crop.pdf}}}
    \hfill
    \caption{Example tweets on Twitter.com}
    \label{figTweetExample}
  }%
\end{figure}

Some example tweets on Twitter are included in Figure \ref{figTweetExample}.
Note how users both add hashtags to the end of a tweet as a summary of the message and emphasize important concepts words in the tweet by turning them into hashtags.
That is, hashtags are both intermixed within the words of the tweet and added to the end of the message.

@@

\begin{figure}[!htbp]
  \scalebox{.4}{\resizebox{\linewidth}{!}{\includegraphics{google+HashtagExample-crop.pdf}}}
  \caption{Example post on google+. The system recommended \emph{\#SFGiants} and \emph{\#BusterPosey} as hashtags for the user-generated post}
  \label{figGoogle+Hashtags}
\end{figure}
